Twisted 11-dimensional supergravity, I

### 2021-09-16 dimred.tex
merge

In this section we wish to demonstrate that our proposal for the interactions for twisted 11-dimensional supergravity agree with conjectural descriptions of twisted type IIA and type I supergravities due to \cite{CLSugra}. We begin by introducing certain variants of Kodaira-Spencer theory which will feature in the descriptions of twists of type IIA and type I.

@@

Let $X$ be a Calabi-Yau manifold. Recall the $\Z/2$ graded Poisson BV theory denoted $\cE_{KS}$ defined in section \surya{}. Let $\cE_{{mKS}}\subset \cE_{KS}$ denote the smallest subcomplex containing those fields with nonzero pairing under the Poisson tensor. Explicitly, we have that $cE_{mKS}$ is the sheaf of cochain complexes
\beqn
\begin{tikzcd}
                        &                          &                                     & {\PV^{0,\bu}}    \\
                        &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
                        & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{3,\bu}} \arrow[r] & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn

Clearly, the inclusion is a Poisson map, so restricting $I_{BCOV}$ to this subcomplex defines another $\Z/2$ graded Poisson BV theory referred to as minimal Kodaira-Spencer theory. Under the identification of Kodaira-Spencer theory as the closed string sector of the B-model, minimal Kodaira-Spencer theory should be thought of as consisting of those closed string fields present in the supergravity approximation.

@@

\begin{conj}
  Let $M$ be a real symplectic surface and $X$ a Calabi-Yau fourfold. The $SU(4)$-invariant twist of type IIA supergravity on $M\times X$ is the $\Z/2$-graded Poisson BV theory with fields \[\Omega^{\bu}(M)\otimes \cE_{mKS}.\] The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
\end{conj}

@@

Our goal is to compare the dimensional reduction of our 11d theory $\cE$ on $\R\times \C^{\times}\times X$ where $X$ is a Calabi-Yau 4-fold with the $SU(4)$ invariant twist of type IIA on $\R^{2}\times X$. Doing so will require some additional modifications to the above conjectural description. Indeed, recall that in the physical theory, the components of the C-field in 11d that are not supported along the M-theory circle become the components of the Ramond-Ramond 2-form of type IIA. However, as noted in \cite{CLSugra} components of Ramond-Ramond fields do not appear as fields in Kodaira-Spencer theory; rather it is components of their field strengths that appear. Since components of the C-field become components of $\gamma$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.

Minimal Kodaira-Spencer theory with potentials on a Calabi-Yau fourfold $X$ is defined to be the $\Z/2$-graded BV theory whose space of fields is the sheaf of cochain complexes $\cE_{pot}$
\beqn
\begin{tikzcd}
& {\PV^{0,\bu}}_\eta  \\
{\PV^{1,\bu}}_\mu \arrow[r, "u\div"] & {u\PV^{0,\bu}}_\nu \\
{u^{-1}\PV^{4,\bu}}_\beta \arrow[r, "u\div"] & {\PV^{3,\bu}}_\gamma  \\
{\PV^{4,\bu}}_\theta &
\end{tikzcd}
\eeqn.

The interaction is given by \[I_{pot} = \int \frac{1}{1-\nu}(\mu\mu\del\gamma + \eta\del\gamma\del\gamma + \eta\mu\del\theta).\]

Note that there is a natural map of cochain complexes $\partial \cE_{pot}\to \cE_{mKS}$ given by the dotted arrows below:
\beqn
\begin{tikzcd}
                                       & {\PV^{0,\bu}} \arrow[rrr, dotted, "\id"] &                          &                                     & {\PV^{0,\bu}}    \\
{\PV^{1,\bu}} \arrow[r, "u\div"]       & {u\PV^{0,\bu}} \arrow[rr, dotted, "\id"] &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
{u^{-1}\PV^{4,\bu}} \arrow[r, "u\div"] & {\PV^{3,\bu}} \arrow[r, dotted, "\div"]  & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{4,\bu}} \arrow[r, dotted, "\div"]        & {\PV^{3,\bu}} \arrow[r]          & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn
This is easily seen to be a Poisson map. We have that $I_{pot} = \partial^{*}I_{BCOV}$, so we see that $I_{pot}$ satisfies the classical master equation. Therefore, $I_{pot}$ determines an $L_{\infty}$ structure on $\cE_{pot}$, and hence one on $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$. In what follows, the $SU(4)$-invariant twist of IIA will refer to the BV theory $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.

\parsec[sec:dimred]
\begin{prop}
The $SU(4)$ invariant twist of type IIA on $\R^{2}\times X$ is the dimensional reduction of the 11d theory $\cE$ on $\R\times \C^{\times}\times X.$
\end{prop}
\begin{proof}
We use the notion of dimensional reduction as defined in \cite{}.
Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$. Note that there is an isomorphism \[\int: \pi^{*}(\Omega^{\bullet}(\R^{2})\otimes \cE_{pot})\to \cE\] given by \[(\eta, \mu, \nu, \beta,\gamma,\theta)\mapsto (\nu = \nu, \mu = \mu + \theta \vee \Omega_{X} \wedge\del_{z}, \beta = \beta, \gamma = \gamma\vee \Omega_{X} \eta dz ).\] It is clear that this isomorphism presrves the BV pairings; we need only check that $\int^{*} I$ is cohomologous to $I_{pot}$ in the deformation-obstruction complex of the free limit of $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.

>>>>

\section{Dimensional reduction and 10-dimensional supergravity}

In this section we demonstrate that our proposal for the action of minimally twisted 11-dimensional supergravity agrees with conjectural descriptions of twisted type IIA and type I supergravities due to Costello and Li.

The original motivation for $M$-theory was as the strong coupling limit for type IIA string theory.
Roughly, the radius of the $M$-theory circle plays the role of this coupling constant. 
Additionally, at low energies $M$-theory is expected to be approximated by 11-dimensional supergravity in the same way that the low energy limit of type IIA/IIB string theory is type IIA/IIB supergravity. 
Combining these two pictures, various checks have been made that the dimensional reduction of 11-dimensional supergravity along the $M$-theory circle is type IIA supergravity.

Motivated by the topological string, Costello and Li have laid out a series of conjectures for twists of type IIA/IIB supergravity \cite{CLsugra} and type I supergravity \cite{CLtypeI}. 
Their description was inspired by the model of the open and closed $B$-model topological string on a Calabi--Yau manifold. 
The open sector is holomorphic Chern--Simons theory \cite{WittenOpen} and the closed sector is called Kodaira--Spencer theory \cite{BCOV}. 
There are a few different versions of Kodaira--Spencer theory, but the shared characteristic is that they are all `gravitational' in nature; they describe fluctuations of the Calabi--Yau structure. 
From this point of view, Kodaira--Spencer theory is at the heart of the formulation of the various flavors of twisted 10-dimensional supergravity.

We begin by introducing certain variants of Kodaira--Spencer theory which will feature in the descriptions of twists of type IIA and type I supergravity.

\subsection{Kodaira--Spencer theory}

Let $X$ be a Calabi--Yau manifold; for now it can be of arbitrary complex dimension. 
Define
\deq{
  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
}
We will consider the graded space $\PV^{\bu,\bu}(X) = \oplus_{i,j} \PV^{i,j}(X)[-i-j]$ where the piece of type $(i,j)$ sits in degree $i+j$.

For each fixed $i$, while we let $j$ vary, the $\dbar$ operator defines a cochain complex $\PV^{i,\bu}(X) = (\oplus_j\PV^{i,j}(X) [-j], \dbar)$ which provides a resolution for the sheaf of holomorphic polyvector fields of type $i$. 
The divergence operator extends to an operator of the form
\[
\div \colon \PV^{i,\bu}(X) \to \PV^{i-1,\bu}(X) .
\]

Motivated by the states of the topological $B$-model, one defines the fields of Kodaira--Spencer gravity on $X$ to be the cochain complex
\beqn\label{eqn:ks1}
\left(\PV^{\bu,\bu} (X)[[u]] [2] \, , \, \dbar + u \div\right) .
\eeqn 
Here, $u$ is a parameter of cohomological degree $+2$, which turns $\delta_{KS}^{(1)} = \dbar + u \div$ into an operator of homogenous degree $+1$. 
We also have performed an overall cohomological shift by $2$ so that $u^k \PV^{i,j}$ sits in degree $i+j+2k-2$. 
More precisely, this is a model for the $S^1$-equivariant cohomology of the states of the $B$-model on a closed disk. 
We refer to \cite{CLtypeI, CLsugra} for detailed justification for this ansatz.

\brian{surya, could fill these parsecs in?}

\parsec[s:poisson]

%describe odd poisson structure

\parsec[s:ksaction]

%recall genus zero BCOV action.

\parsec[s:minimalks]

%define minimal ks

\subsection{The $SU(4)$ twist of type IIA supergravity}

@@

Let $X$ be a Calabi-Yau manifold of complex dimension four. 
The complex of fields of minimal Kodaira--Spencer theory on $X$ takes the form
\beqn
\begin{tikzcd}
                        &                          &                                     & {\PV^{0,\bu}}    \\
                        &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
                        & {\PV^{2,\bu}} \arrow[r, "u\div"]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
{\PV^{3,\bu}} \arrow[r, "u\div"] & {u\PV^{2,\bu}} \arrow[r, "u\div"] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
\end{tikzcd}.
\eeqn
Denote this complex by $\cE_{mKS}(X)$. 
The classical BCOV action $I_{BCOV}$ follows from the general formula we gave above.

\brian{I've commented this out below, since we should just introduce minimal BCOV in general up above}

%Clearly, the inclusion is a Poisson map, so restricting $I_{BCOV}$ to this subcomplex defines another $\Z/2$ graded Poisson BV theory referred to as minimal Kodaira-Spencer theory. Under the identification of Kodaira-Spencer theory as the closed string sector of the B-model, minimal Kodaira-Spencer theory should be thought of as consisting of those closed string fields present in the supergravity approximation.

@@

\begin{conj}
The $SU(4)$-invariant twist of type IIA supergravity on $\RR^2\times \CC^4$ is the $\Z/2$-graded Poisson BV theory with fields \[
\alpha = \sum_n \alpha_n u^n \in \cE_{mKS}(\CC^4) \otimes \Omega^{\bu}(\RR^2).\] 
The classical interaction takes the form $I_{IIA} = \int_{\CC^4 \times \RR^2} \alpha_0^3 + {\rm higher\;order\;terms}.$
%The $L_{\infty}$ structure is the natural one on the tensor product of the cdga $\Omega^{\bu}(M)$ with the $L_{\infty}$-algebra $\cE_{mKS}$.
\end{conj}

We will need a more detailed description of the classical action. 
For the moment, let us introduce some notations for the fields of this IIA model, as always we leave the internal Dolbeault degree implicit:
\begin{multline}
\eta \in \PV^{0,\bu}(\CC^4) \otimes \Omega^\bu (\RR^2), \quad \mu + u \nu \in \PV^{1, \bu}(\CC^4) \otimes \Omega^\bu (\RR^2) \oplus u \PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2) \\
\Pi \in \PV^{3,\bu}(\CC^4) \otimes \Omega^\bu(\RR^2), \quad \sigma \in \PV^{3,\bu}(\CC^4) \otimes \Omega^\bu (\RR^2) .
\end{multline}
We will not need an explicit notation for the remaining descendant fields.

With this notation in hand, we have the more precise form of the action appearing in the conjecture:
\beqn\label{eqn:IIAaction}
I_{IIA} = \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \wedge \Pi + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \mu \wedge \sigma + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \Pi^2 + \cdots 
\eeqn
where the $\cdots$ denote terms involving higher order descendants.

@@

Our goal is to compare the dimensional reduction of our 11-dimensional theory on $\CC^5 \times \RR$
%where $X$ is a Calabi-Yau 4-fold 
with the $SU(4)$ invariant twist of type IIA on $\R^{2}\times \CC^4$. 
Doing so will require some additional modifications to the above conjectural description.

Recall that in the physical theory, the components of the $C$-field in 11d that are not supported along the M-theory circle become the components of the Ramond--Ramond 2-form of type IIA. However, as noted in \cite{CLSugra} components of Ramond--Ramond fields do not appear as fields in Kodaira--Spencer theory; rather it is components of their field strengths that appear. Since components of the $C$-field become components of $\gamma$ in $\cE$ \surya{hopefully we can see this in the component fields section}, this suggests that we must modify our description of the twist of type IIA to include potentials for certain fields.

Explicitly, to define this theory we introduce a potential for both the $\Pi$ and $\sigma$ fields. 
First, we introduce a field $\gamma$ (not to be confused, yet, with the $\gamma$ field in our 11-dimensional theory) which satisfies $\Pi = \div \gamma$.
This condition does not uniquely fix $\gamma$. 
There is a new linear gauge symmetry determined by $\gamma \to \gamma + \div \beta$ where $\beta$ is a ghost that we must also introduce. 
Similarly, we introduce a field $\theta$ which satisfies $\sigma = \div \theta$, there is no extra gauge symmetry present in this condition.

In diagrammatic detail, the potential theory we are considering has underlying cochain complex of fields
\beqn\label{eqn:IIApot}
\begin{tikzcd}
- & + \\ \hline
& {\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2) }_\eta  \\
{\PV^{1,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\mu \arrow[r, "u\div"] & u{\PV^{0,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\nu \\
u^{-1}{\PV^{4,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\beta \arrow[r, "u\div"] & {\PV^{3,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\gamma  \\
{\PV^{4,\bu} (\CC^4) \otimes \Omega^\bu (\RR^2)}_\theta &
\end{tikzcd}
\eeqn.

Recall that the original fields of the IIA supergravity model on $\CC^4 \times \RR^2$ was equipped with an odd Poisson bivector which was degenerate.
In other words, it did not define a theory in the conventional BV formalism. 
One of the key features of this new complex of fields, after we have taken these potentials, is that it is equipped with an odd non-degenerate pairing thus equipping it with the structure of a theory in the conventional BV formalism.

The pairing is $\Res_u \frac{\d u}{u} \int^\Omega_{\CC^4 \times \RR^2} \alpha \wedge \alpha'$ where $\alpha, \alpha'$ are two general fields in this potential theory on $\CC^4 \times \RR^2$. 
Explicitly, in the description of the fields in \eqref{eqn:IIApot} the pairing is 
\[
\int^\Omega_{\CC^4 \times \RR^2} \eta \wedge \theta + \int^\Omega_{\CC^4 \times \RR^2} \mu \wedge \gamma + \int^\Omega_{\CC^4 \times \RR^2} \nu \wedge \beta .
\]
This pairing is compatible with the odd Poisson bracket present in the original theory on $\CC^4 \times \RR^2$. \brian{finish}

The type IIA action completely determines the action of this theory with potentials. 
One simply takes the \eqref{eqn:IIAaction} and replaces all appearances of $\Pi$ with $\div \gamma$ and all appearances of $\sigma$ with $\div \theta$. 
This yields the interaction of the potential theory
\beqn\label{eqn:IIAactionpot}
\til I_{IIA} = \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \mu^2 \wedge \div \gamma + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \mu \wedge \div \theta + \int^\Omega_{\CC^4 \times \RR^2} \frac{1}{1-\nu} \eta \wedge \div \gamma \wedge \div \gamma 
\eeqn
Notice that the terms involving higher descendants vanishes since these fields are set to zero in the potential theory.

%Note that there is a natural map of cochain complexes $\partial \cE_{pot}\to \cE_{mKS}$ given by the dotted arrows below:
%\beqn
%\begin{tikzcd}
%                                       & {\PV^{0,\bu}} \arrow[rrr, dotted, "\id"] &                          &                                     & {\PV^{0,\bu}}    \\
%{\PV^{1,\bu}} \arrow[r, "u\div"]       & {u\PV^{0,\bu}} \arrow[rr, dotted, "\id"] &                          & {\PV^{1,\bu}} \arrow[r, "u\div"]    & {u\PV^{0,\bu}}   \\
%{u^{-1}\PV^{4,\bu}} \arrow[r, "u\div"] & {\PV^{3,\bu}} \arrow[r, dotted, "\div"]  & {\PV^{2,\bu}} \arrow[r]  & {u\PV^{1,\bu}} \arrow[r, "u\div"]   & {u^2\PV^{0,\bu}} \\
%{\PV^{4,\bu}} \arrow[r, dotted, "\div"]        & {\PV^{3,\bu}} \arrow[r]          & {u\PV^{2,\bu}} \arrow[r] & {u^2\PV^{1,\bu}} \arrow[r, "u\div"] & {u^3\PV^{0,\bu}}
%\end{tikzcd}.
%\eeqn
%This is easily seen to be a Poisson map. We have that $I_{pot} = \partial^{*}I_{BCOV}$, so we see that $I_{pot}$ satisfies the classical master equation. Therefore, $I_{pot}$ determines an $L_{\infty}$ structure on $\cE_{pot}$, and hence one on $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$. In what follows, the $SU(4)$-invariant twist of IIA will refer to the BV theory $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.

\parsec[sec:dimred]

We turn to the proof of the main result of this section that the dimensional reduction of our 11-dimensional theory agrees with the twist of IIA supergravity just introduced.

We recall the notion of dimensional along a holomorphic direction following \cite{ESW}. 
Suppose that $V_\RR$ is a real vector space and denote by $V$ its complexification. 
We consider a field theory defined on $M \times V$, which is holomorphic along $V$ (in particular, this means that the theory is translation invariant along $V$).  
We consider the dimensional reduction along the projection 
\beqn\label{eqn:dimred}
M \times V \to M \times V_\RR
\eeqn
induced by ${\rm Re} \colon V \to V_\RR$.
Most relevant for us is the case when $V = \CC$ and $M$ is $\CC^4 \times \RR$, but the explicit form of the theory along $M$ is not important at the moment.

In fact, we might as well assume that $M$ is a point and that the space of fields is of the form $\Omega^{0,\bu}(V) \otimes W$ for $W$ some graded vector space. 
As properly formulated in \cite{ESW}, it is shown that the dimensional reduction along $V \to V_\RR$ is equivalent to the theory whose fields are $\Omega^\bu(V_\RR) \otimes W$. 
In other words, the dimensional reduction of the holomorphic theory on $V$ is a topological theory on $V_\RR$.

If we put $M$ back in, the result is similar. 
Suppose the original theory is of the form $\cE(M) \otimes \Omega^{0,\bu}(V) \otimes W$.
Then, the dimensional reduction along \eqref{eqn:dimred} is the theory whose space of fields is $\cE(M) \otimes \Omega^\bu(V_\RR) \otimes W$.

An explicit model for this reduction can be described as follows. 
Suppose $V \cong \CC^n$ and place the theory on $(\CC^\times)^{\times n} \subset \CC^n$. 
The dimensional reduction along $\CC^n \to \RR^n$ agrees with the compactification of the theory along $S^1 \times \cdots \times S^1$ where one throws away all nonzero winding modes around each circle.

\begin{prop}
The $SU(4)$ invariant twist of type IIA on $\CC^4 \times \RR^2$ is equivalent to the dimensional reduction of the 11-dimensional along  
\[
\CC^4 \times \CC \times \RR \to \CC^4 \times \RR \times \RR \cong \CC^4 \times \RR^2 .
\]
\end{prop}
\begin{proof}
Let $\pi : \R\times \C^{\times}\times X \to \R^{2}\times X$ be the projection with fiber $S^{1}\subset \C^{\times}$. Note that there is an isomorphism \[\int: \pi^{*}(\Omega^{\bullet}(\R^{2})\otimes \cE_{pot})\to \cE\] given by \[(\eta, \mu, \nu, \beta,\gamma,\theta)\mapsto (\nu = \nu, \mu = \mu + \theta \vee \Omega_{X} \wedge\del_{z}, \beta = \beta, \gamma = \gamma\vee \Omega_{X} \eta dz ).\] It is clear that this isomorphism presrves the BV pairings; we need only check that $\int^{*} I$ is cohomologous to $I_{pot}$ in the deformation-obstruction complex of the free limit of $\Omega^{\bu}(\R^{2})\otimes \cE_{pot}$.

### 2021-09-16 draft.tex
merge

%\section{Symmetries of the 11-dimensional theory}
\input{dfn}

@@

%Can we try to roughly say where each of our twisted fields come from in the untwisted theory? I imagine this section being pretty chill and mostly to orient physicists. 
\input{suco}

@@

@@

\parsec

As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and Poisson Chern-Simons. We will find a match between indices counting local operators supported at a point.

Consider the cartan subalgebra of the bosonic part of $\lie{osp}(6|1)$. Explicitly, the action of this subalgebra on the fields of the holomorphic twist is induced from an action on $\C^5$ with weights as in the following table

\[\begin{array}{|c|c|c|c|c|c|}
& z_1 & z_2 & z_3 & w_1 & w_2 \\
\hline
q & & & & 1 & -1 \\
t_1 & 1 & -1 & & & \\
t_2 & & 1 & -1 & & \\
y & -1 & -1 & -1 &\frac 3 2 & \frac 3 2
\end{array}\]

We wish to compute the character of the space of holomorphic local operators $\Obs_0$ with respect to the above action. We first identify a convenient basis for the space of holomorphic local operators. Note that the vector space of solutions to the linearized unconstrained equations of motion is parametrized by 
\begin{align*}
\mu^{z_i} & \in \cO(\C^5)\partial_{z_i},\ \ \ \ \ \mu^{w_j}\in\cO (\C^5)\partial_{w_j}  \\
\nu & \in \cO (\C^5) \\
\gamma^{z_i} & \in \cO (\C^5)dz_i, \ \ \ \ \ \gamma^{w_j}\in\cO (\C^5)d_{w_j} \\
\beta & \in \cO (\C^5)
\end{align*}

Corresponding to each of the above, we have a tower of linear local operators labeled by $(m_i, n_j) = (m_1, m_2, m_3, n_1,  n_2)\in \Z^5_{\geq 0}$; these are given by
\begin{align*}
\mu^{z_i/w_j}_{(m_i, n_j)} &: \mu^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\mu^{z_i/w_j} (0) \\
\nu_{(m_i, n_j)} &: \nu\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\nu (0) \\
\gamma^{z_i/w_j}_{(m_i, n_j)} &: \gamma^{z_i/w_j}\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\gamma^{z_i/w_j} (0) \\
\beta_{(m_i, n_j)} &: \beta\mapsto \partial_{z_1}^{m_1}\partial_{z_2}^{m_2}\partial_{z_3}^{m_3}\partial_{w_1}^{n_1}\partial_{w_2}^{n_2}\beta (0) \\
\end{align*}

With this basis in hand we can readily compute the character. 
\begin{lem}
\[\chi (\Obs_0) = \frac{t_1^{-1}y+ t_1t_2^{-1}y+t_2y+q^{-1}y^{-3/2}+qy^{-3/2}-t_1y- t_1^{-1}t_2y^{-1}-t_2^{-1}y^{-1}-qy^{3/2}-q^{-1}y^{3/2}}{(1-t_1^{-1}y)(1-t_1t_2^{-1}y)(1-t_2y)(1-q^{-1}y^{-3/2})(1-qy^{-3/2})}.\]
\end{lem}

>>>>

\input{dfn}

@@

\input{dimred}

@@

\input{suco}

@@

\input{index}
